% main.tex — Master compilation file
% Paper: "Tokenized Housing and Lifecycle Portfolio Choice:
%         A Decoupling of Location from Housing Exposure"
%
% Target journal: Review of Financial Studies (RFS); backup RAPS / REE.
% Status: skeleton sections complete (s1–s6); [PLACEHOLDER] cells await server1 results.
%
% Compile: pdflatex main.tex  (or lualatex / xelatex)
%          bibtex main
%          pdflatex main.tex  (twice for cross-references)
%
% Or with latexmk:
%   latexmk -pdf main.tex

\documentclass[12pt]{article}

% ─── Packages ───────────────────────────────────────────────────────────────
\usepackage[margin=1.2in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{appendix}
\usepackage{textcomp}   % \textsubscript

% ─── Layout ─────────────────────────────────────────────────────────────────
\onehalfspacing
\setlength{\parskip}{0pt}
\setlength{\parindent}{1.5em}

% ─── Theorem environments ────────────────────────────────────────────────────
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{assumption}{Assumption}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

% ─── Placeholder command ─────────────────────────────────────────────────────
% Usage: \ph{description}  — red placeholder for numerical results pending server1
\newcommand{\ph}[1]{\textcolor{red}{\textsc{[#1]}}}

% ─── Custom commands ─────────────────────────────────────────────────────────
\newcommand{\cev}{\mathrm{CEV}}
\newcommand{\xprev}{x_{\mathrm{prev}}}
\newcommand{\xnew}{x_{\mathrm{new}}}
\newcommand{\tausell}{\tau_{\mathrm{sell}}}
\newcommand{\taubuy}{\tau_{\mathrm{buy}}}
\newcommand{\tautoken}{\tau_{\mathrm{token}}}
\newcommand{\preloc}{p_{\mathrm{reloc}}}
\newcommand{\rhoAB}{\rho_{AB}}
\newcommand{\deltaown}{\delta_{\mathrm{own}}}
\newcommand{\ellA}{\ell_A}
\newcommand{\ellB}{\ell_B}
\newcommand{\EsubzeroTwoL}{\text{E0}}
\newcommand{\EonesubTwoL}{\text{E1}_{\text{2L}}}
\newcommand{\EtwosubTwoL}{\text{E2}_{\text{2L}}}

% ─── Bibliography style ───────────────────────────────────────────────────────
% RFS uses author-year citations.
\bibliographystyle{plainnat}

% ─────────────────────────────────────────────────────────────────────────────
\begin{document}
% ─────────────────────────────────────────────────────────────────────────────

\title{Tokenized Housing and Lifecycle Portfolio Choice:\\
       A Decoupling of Location from Housing Exposure%
       \thanks{We thank seminar participants for helpful comments.
               All errors are our own.
               Code and replication files at \url{https://github.com/[repo]}.}}

\author{[Authors]}

\date{May 2026\\\textit{Preliminary and incomplete — do not cite or circulate.}}

\maketitle

% ─── Abstract ────────────────────────────────────────────────────────────────
\begin{abstract}
We quantify the lifetime welfare value of residential housing tokenization
using a calibrated two-location lifecycle portfolio model with stochastic
relocation shocks.
Households choose among three regimes: rent-only, traditional binary
homeownership (with 8.5\% round-trip transaction cost at each relocation),
and continuous fractional token ownership portable across locations.
The model tracks prior-period token holdings as explicit state variables,
which creates a forward-looking motive to pre-accumulate tokens of a future
destination before relocating.
Our headline result is $\cev(\EtwosubTwoL\ \text{vs}\ \EonesubTwoL)
= \ph{X.XX}\%$ at baseline calibration
($p_{\text{reloc}} = 6\%$, $\taubuy = 2.5\%$, $\rhoAB = 0.50$).
The total gain decomposes into an avoided-transaction-cost channel (\ph{X}\%)
from escaping the forced sell-and-buy round-trip, and a pre-buying hedge
channel (\ph{X}\%) that is uniquely activated by token portability: by
pre-accumulating tokens of the destination location, households reduce the
marginal buying cost on future relocation.
Falsification tests confirm the mechanism: the hedge channel collapses when
the relocation probability is zero and attenuates as cross-location
correlations approach one.
This constitutes a structurally novel welfare channel outside of
\citet{Liu2021}, \citet{YaoZhang2005}, and \citet{KMW2018}.
\end{abstract}

\medskip
\noindent\textbf{Keywords:} tokenized housing; lifecycle portfolio choice;
relocation; transaction costs; household finance; blockchain.\\[2pt]
\noindent\textbf{JEL codes:} G11; G51; R21; R31.

\clearpage

% ─────────────────────────────────────────────────────────────────────────────
\input{sections/s1_intro}
% ─────────────────────────────────────────────────────────────────────────────

\clearpage

% ─────────────────────────────────────────────────────────────────────────────
\input{sections/s2_model}
% ─────────────────────────────────────────────────────────────────────────────

\clearpage

% ─────────────────────────────────────────────────────────────────────────────
\input{sections/s3_calibration}
% ─────────────────────────────────────────────────────────────────────────────

\clearpage

% ─────────────────────────────────────────────────────────────────────────────
\input{sections/s4_results}
% ─────────────────────────────────────────────────────────────────────────────

\clearpage

% ─────────────────────────────────────────────────────────────────────────────
\input{sections/s5_discussion}
% ─────────────────────────────────────────────────────────────────────────────

\clearpage

% ─────────────────────────────────────────────────────────────────────────────
\input{sections/s6_conclusion}
% ─────────────────────────────────────────────────────────────────────────────

\clearpage

% ─── References ──────────────────────────────────────────────────────────────
\bibliography{references}

% ─────────────────────────────────────────────────────────────────────────────
\clearpage
\begin{appendices}
% ─────────────────────────────────────────────────────────────────────────────

\section{Numerical Implementation Details}
\label{app:numerical}

\subsection{Value function iteration}

The Bellman equation is solved by backward induction over periods $t = T, T-1,
\ldots, 1$.
Each period, we iterate over the 6-dimensional state grid $(w, z, \ell,
x_{A,\text{prev}}, x_{B,\text{prev}})$ with $T = 56$ periods (ages 25--80).
The continuation value is approximated by 7-dimensional Gauss-Hermite
quadrature with $n = 3$ nodes per dimension ($3^7 = 2{,}187$ quadrature points),
integrating jointly over the stock return, aggregate housing factor, two
idiosyncratic location shocks, house-price normalisation, permanent income shock,
and transitory income shock.

\subsection{Interpolation}

Continuation values are computed by bilinear interpolation over the $(w, z)$
grid dimensions.
The $(x_{A,\text{prev}}, x_{B,\text{prev}})$ dimensions are indexed exactly:
by restricting the choice of $x_{\text{new}}$ to the $x_{\text{prev}}$ grid,
the next-period state is always an exact grid point, eliminating the need to
interpolate over the $x_{\text{prev}}$ dimensions.

\subsection{Coarse grid and computation time}

Baseline grids: $N_W = 15$, $N_Z = 5$, $N_{x,\text{prev}} = 3$,
$N_{\ell} = 2$, giving $15 \times 5 \times 2 \times 3 \times 3 = 1{,}350$
states per period.
Control search: $N_{\text{asset}} = 7$ points for $b$ and $s$ candidates;
$N_{x,\text{prev}} = 3$ choices for each of $x_{A,\text{new}}$ and
$x_{B,\text{new}}$ (9 combinations in E2\textsubscript{2L}).
Estimated wall time per regime at baseline: \ph{X} hours on [server1 spec].
Full-grid runs use $N_W = 40$, $N_Z = 9$, $N_{x,\text{prev}} = 5$ and are
used for robustness checks.

\section{Convergence Diagnostics}
\label{app:convergence}

\ph{To be populated from output/diagnostics/p6\_option1\_smoke.md after server1 run.}

Table~\ref{tab:convergence} reports Euler-residual statistics and
value-function sup-norm convergence at the coarse and full grids.

\begin{table}[h]
\centering
\caption{Convergence diagnostics \ph{(placeholder — fill from server1 output)}}
\label{tab:convergence}
\begin{tabular}{lcc}
\toprule
Metric & Coarse grid & Full grid \\
\midrule
Feasible states at $t=1$ (\%) & \ph{X} & \ph{X} \\
Euler residual p50             & \ph{X} & \ph{X} \\
Euler residual p95             & \ph{X} & \ph{X} \\
NaN / Inf health check         & PASS   & \ph{TBD} \\
Terminal-identity check        & PASS   & \ph{TBD} \\
\bottomrule
\end{tabular}
\end{table}

\section{Hedge-Channel Sign Conditions}
\label{app:sign}

\begin{proposition}[Necessary condition for a positive pre-buying hedge channel]
\label{prop:sign}
In regime \EtwosubTwoL, a household at location~$A$ holds $x_{B,\text{new}} > 0$
in equilibrium if and only if the expected present value of future buying-cost
savings exceeds the current opportunity cost of holding a non-occupied token:
\begin{equation}
  \underbrace{p_{\text{reloc}} \cdot \taubuy}_{\text{expected saving per unit}}
  >
  \underbrace{\delta_{\text{own}} - \mathbb{E}[R_B - R_f]}_{\text{opportunity cost of }x_B \text{ over bond}},
  \label{eq:sign_condition}
\end{equation}
where $\delta_{\text{own}} = \rho - m$ is the rent-saving forgone by holding a
non-occupied unit, and $\mathbb{E}[R_B - R_f]$ is the expected excess return
on location-B housing.
\end{proposition}

\begin{remark}
At baseline calibration: $p_{\text{reloc}} \cdot \taubuy = 0.06 \times 0.025 =
0.0015$ per period per unit; $\delta_{\text{own}} = 0.04$;
$\mathbb{E}[R_B - R_f] = \ph{X}$.
The sign of the hedge channel is therefore an empirical question, resolved by
the server1 baseline runs.
If the condition holds, $x_{B,\text{new}} > 0$ at ell=A (H1 confirmed);
if it fails, the channel is inactive (fall back to Path~D).
\end{remark}

\end{appendices}

% ─────────────────────────────────────────────────────────────────────────────
\end{document}
% ─────────────────────────────────────────────────────────────────────────────
